ext_risk_copula

### 2019-01-21 ext_risk_copula.Rmd
adding msmith d0_extrisk_vs_r plot

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (ricker model with no dispersion : rc=1); numlocs=5, numsteps=25, numsims=10000\label{fig_ricker__risk_global_disp}](./Results/ricker/ricker_extrisk_d0.pdf){ width=40%, height=40% }

@@

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (hassell model with no dispersion : rc=2.73199); numlocs=5, numsteps=25, numsims=10000\label{fig_ricker__risk_global_disp}](./Results/hassell/hassell_extrisk_d0.pdf){ width=40%, height=40% }

@@

rlist<-seq(from=1.2,to=2.8,by=0.2)
numsims<-10000
numsteps<-25
numlocs<-5
a<-1
b<-3
scl<-1

#msmith_extrisk_d0<-data.frame(rlist,NA*numeric(length(rlist)),NA*numeric(length(rlist))) #initiate a dataframe to store ext risk at dispersal d=0 for all r
#colnames(msmith_extrisk_d0)<-c("r","risk_left_d0","risk_right_d0")

# plot for local dispersal in D matrix 
pdf(paste(resloc,"msmith_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.2))
for(r in rlist){
    K_e<-((r-1)^(1/b))/a
    K<-K_e
    ext_thrs<-K/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,r=r,K=K,a=a,b=b,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

# plot for global dispersal in D matrix 
pdf(paste(resloc,"msmith_ext_risk_global_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.2))
for(r in rlist){
    K_e<-((r-1)^(1/b))/a
    K<-K_e
    ext_thrs<-K/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,r=r,K=K,a=a,b=b,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()
```

@@

>>>>

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (ricker model with no dispersion : rc=1); numlocs=5, numsteps=25, numsims=10000\label{fig_ricker_risk_d0}](./Results/ricker/ricker_extrisk_d0.pdf){ width=40%, height=40% }

@@

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (hassell model with no dispersion : rc=2.73199); numlocs=5, numsteps=25, numsims=10000\label{fig_hassell_risk_d0}](./Results/hassell/hassell_extrisk_d0.pdf){ width=40%, height=40% }

@@

numsims<-10000
numsteps<-25
numlocs<-5
a<-0.5
b<-4
scl<-1

rc<-b/(b-1)
rlist<-sort(c(seq(from=1.2,to=2.8,by=0.2),rc))

msmith_extrisk_d0<-data.frame(rlist,NA*numeric(length(rlist)),NA*numeric(length(rlist))) #initiate a dataframe to store ext risk at dispersal d=0 for all r
colnames(msmith_extrisk_d0)<-c("r","risk_left_d0","risk_right_d0")

# plot for local dispersal in D matrix 
pdf(paste(resloc,"msmith_ext_risk_local_disp.pdf",sep=""),height=9,width=12)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,1.2))
for(i in c(1:length(rlist))){
    r<-rlist[i]
    K_e<-((r-1)^(1/b))/a
    K<-K_e
    ext_thrs<-K/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,r=r,K=K,a=a,b=b,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,ploton = F)
    msmith_extrisk_d0$risk_left_d0[i]<-s$risk_left[1]
    msmith_extrisk_d0$risk_right_d0[i]<-s$risk_right[1]
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()

saveRDS(msmith_extrisk_d0,paste(resloc,"msmith_extrisk_d0.RDS",sep=""))

# plot for global dispersal in D matrix 
pdf(paste(resloc,"msmith_ext_risk_global_disp.pdf",sep=""),height=9,width=12)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,1.2))
for(r in rlist){
    K_e<-((r-1)^(1/b))/a
    K<-K_e
    ext_thrs<-K/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,r=r,K=K,a=a,b=b,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,ploton = F)
    plot(s$d_seq,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",panel.first = grid(),xlab="d",ylab="ext_risk",cex.lab=1.5,cex.axis=1.5)
    lines(s$d_seq,s$risk_right,type="b",col="blue")
    legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
    mtext(paste0("r = ", r))
}
par(op)
dev.off()
```

```{r fig_msmith_extrisk_d0, echo=F,results="hide"}
set.seed(seed)
numsims<-10000
msmith_extrisk_d0<-readRDS("./Results/msmith/msmith_extrisk_d0.RDS")

msmith_extrisk_d0$CI0.025left<-qbinom(msmith_extrisk_d0$risk_left_d0,size=numsims,prob=0.025)/numsims
msmith_extrisk_d0$CI0.975left<-qbinom(msmith_extrisk_d0$risk_left_d0,size=numsims,prob=0.975)/numsims

msmith_extrisk_d0$CI0.025right<-qbinom(msmith_extrisk_d0$risk_right_d0,size=numsims,prob=0.025)/numsims
msmith_extrisk_d0$CI0.975right<-qbinom(msmith_extrisk_d0$risk_right_d0,size=numsims,prob=0.975)/numsims

pdf("./Results/msmith/msmith_extrisk_d0.pdf",height = 6,width=6)
plot(msmith_extrisk_d0$r,msmith_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),xlim = c(1.2,2.8),xlab="r",ylab="ext_risk",cex.lab=1.5,pch=1)
arrows(x0=msmith_extrisk_d0$r,y0=msmith_extrisk_d0$CI0.025left,x1=msmith_extrisk_d0$r,y1=msmith_extrisk_d0$CI0.975left,angle=90,length=0.05,col=rgb(1,0,0,0.5),code=3)

lines(msmith_extrisk_d0$r,msmith_extrisk_d0$risk_right_d0,col="blue",type="b",ylim=c(0,1),pch=1)
arrows(x0=msmith_extrisk_d0$r,y0=msmith_extrisk_d0$CI0.025right,x1=msmith_extrisk_d0$r,y1=msmith_extrisk_d0$CI0.975right,angle=90,length=0.05,col=rgb(0,0,1,0.5),code=3)
mtext(paste0("d = 0 , numsims = ",numsims),side=3,line=0.2)
legend(1.5,1.08, c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), col=c('red', 'blue'), horiz=T, bty='n',cex=1.2)

@@

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Maynard Smith model with no dispersion : rc=1.33); numlocs=5, numsteps=25, numsims=10000\label{fig_msmith_risk_d0}](./Results/msmith/msmith_extrisk_d0.pdf){ width=40%, height=40% }
